### 2015-12-12 fundamentals/fcsreqs.tex
going for brevity, I delete unneccessary uses of words like very and currently.

Modularity is a key enabler of extending the scope of fuel cycle analysis
within the \Cyclus framework.  Changes that are required to improve the
fidelity of modeling a particular agent, or to introduce entirely new agents,
are narrowly confined and place no new requirements on the \Cyclus kernel.
Furthermore, there are very few assumptions or heuristics that would otherwise
restrict the algorithmic complexity that can be used to model the behavior of
such agents.

>>>>

Modularity is a key enabler of extending the scope of fuel cycle analysis
within the \Cyclus framework.  Changes that are required to improve the
fidelity of modeling a particular agent, or to introduce entirely new agents,
are narrowly confined and place no new requirements on the \Cyclus kernel.
Furthermore, there are few assumptions or heuristics that would otherwise
restrict the algorithmic complexity that can be used to model the behavior of
such agents.

### 2015-12-12 fundamentals/impl.tex
going for brevity, I delete unneccessary uses of words like very and currently.

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.  
For the archetype developer, these interfaces provide enormous power
very simply. The \gls{API} abstracts away details unnecessary to specifying the 
archetype behavior, while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.
For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
in a simulation.

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials store the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 3 decay modes, with 1 additional
mode likely to be added in a future release:

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.

>>>>

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \glspl{API} that define agent-to-agent interaction as well as agent-to-environment interaction.
For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.  
For the archetype developer, these interfaces provide enormous power
simply. The \gls{API} abstracts away details unnecessary to specifying the 
archetype behavior, while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.
For the user, multiple archetypes that inherit the same \glspl{API} are interchangeable
in a simulation.

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials store the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can operate in 3 decay modes, with 1 additional
mode likely to be added in a future release:

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.
